PACE 2024: OCMu64, reductions and a branch-and-bound solver for\\ One-sided Crossing Minimization

### 2024-09-03 tex/poster.tex
drop comment
shrink fig
fix too small text
Fix name typo, lemma -> result

\author{Ragnar {Groot Koerkamp} \inst{1} \and Mees de vries \inst{2}}

@@

        \textbf{The lemma is optimal:}
        Without further assumptions on $(A, <)$ or on the other elements of $B$, it is not
          possible to prove $u \b v$ if $(u, v)$ is not strongly fixed.
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$. Now take sets of vertices $L, M,
          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with
          $\max(N(u)) < R$.
          Add a node $x \in B$ connected to $L$, $M$, $R$. With the correct numbers of vertices in
          $L$, $M$, $R$ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
        $v$ has to go before $u$.

        \centering
          \vspace{-0.5em}
        \includegraphics[scale=2]{fig/blocking-set.pdf}
          \vspace{-1em}

@@

        \textbf{Blocking set:}
        Suppose $r(u,v)< 0$, i.e., $u$ wants to go left of $v$.
        A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) \leq \min(c(v, u,
        X), (X, v, u))$.  If there is no blocking set for $(u, v)$, we call it a
        \emph{practically fixed pair}, and $u\b v$.
      \end{block}

@@

        \ragnar{A figure of prefix and tail and optimal insert here would be
          nice to make the section less boring.}

>>>>

\author{Ragnar {Groot Koerkamp} \inst{1} \and Mees de Vries \inst{2}}

@@

        \textbf{This result is optimal:}
        Without further assumptions on $(A, <)$ or on the other elements of $B$, it is not
          possible to prove $u \b v$ if $(u, v)$ is not strongly fixed.
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$. Now take sets of vertices $L, M,
          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with
          $\max(N(u)) < R$.
          Add a node $x \in B$ connected to $L$, $M$, $R$. With the correct numbers of vertices in
          $L$, $M$, $R$ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
        $v$ has to go before $u$.

        \centering
          \vspace{-0.5em}
        \includegraphics[scale=1.5]{fig/blocking-set.pdf}
          \vspace{-1em}
      \end{block}

        \textbf{Blocking set:}
        Suppose $r(u,v)< 0$, i.e., $u$ wants to go left of $v$.
        A \emph{blocking set} $X\subseteq B-\{u,v\}$ is a set such that $c(v,X,u) \leq \min(c(v, u,
        X), (X, v, u))$.  If there is no blocking set for $(u, v)$, we call it a
        \emph{practically fixed pair}, and $u\b v$.

@@

@@
